---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# R-LIMS

<!-- badges: start -->
<!-- badges: end -->

R-LIMS is an R package for interacting with D-LIMS. D-LIMS is an internal SQL database at the Manchester Genomic Laboratory Hub which is used for logging samples, organising testing, recording results and writing genetic reports.

R-LIMS consists of useful functions for connecting and querying D-LIMS with R using an odbc connection, with dplyr queries automatically converted into SQL queries with the dbplyr package.

R-LIMS aims to simplify and streamline interacting with D-LIMS at scale, for development projects and for audits.

## Installation

You can install the development version of rlims from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joeshaw824/rlims")
```

Using rlms requires you have to have to have an ODBC connection to the DLIMS server already set up on your computer, for which you will need to be granted permissions by the database owner. Please contact me if you have any issues with this.

## Example

To begin with, you can set up the ODBC connection which connects to the server mirror version of the DLIMS database using `connect_odbc()`.

Note: the get_columns function currently relies on a deprecated function which I need to fix.

```{r example}
library(rlims)

# Set up the odbc connection
connect_odbc()

# Check the column names for the "Samples" table
head(get_columns("Samples", cols = "narrow"))

```

Alternatively, some functions are stand-alone and are just useful for the kinds of projects I've been working on. For example the parse_ncc function just pulls out the neoplastic cell content from a string of text.

```{r parse-ncc-example}
parse_ncc("Tumour neoplastic cell content was 20% but mutation wasn't found")

```




